---
title: "Analysis"
output: pdf_document
date: "2025-10-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load packages}

library(tidyverse)
library(ggplot2)
library(igraph)
library(kableExtra)
library(webshot2)
library(ggraph)

options("encoding" = "UTF-8")
```

```{r load data}

main_data <- read_csv("data_ready.csv")
distance_data<- read.csv("output_df.csv", header = TRUE, fileEncoding = "UTF-8")
#check <- distance_data %>% dplyr::select(S2CF1.S2CF1, Gloss, IPAactual)
network_graphs <- read_csv("globalsmallworlddata.csv")
```

## Data

```{r summary data - full}

n_infants <- main_data %>% group_by(Subject, Language) %>% tally()
n_langs <- main_data %>% group_by(Language) %>% tally()
age_data <- main_data %>% summarise(mean_age = mean(Age),
                                     min_age = min(Age),
                                     max_age = max(Age),
                                     sd_age = sd(Age))

tokens_data <- n_infants %>% ungroup() %>% summarise(mean_tok = mean(n),
                                       min_tok = min(n),
                                       max_tok = max(n),
                                       sd_tok = sd(n))

types_data <- main_data %>% group_by(Subject, Gloss) %>% tally() %>%
  ungroup() %>%
  group_by(Subject) %>% tally() %>% summarise(mean_typ = mean(n),
                                       min_typ = min(n),
                                       max_typ = max(n),
                                       sd_typ = sd(n))

types_tokens <- main_data %>% group_by(Gloss) %>% tally() %>%
  summarise(n_typ = length(Gloss),
            n_tok = sum(n)) 


```

```{r summary data - disyllables}

disyl_data <- main_data %>% filter(nsyl_target == 2)

types_tokens <- disyl_data %>% group_by(Gloss) %>% tally() %>%
  summarise(n_typ = length(Gloss),
            n_tok = sum(n)) 

mean_tok_disyl <- disyl_data %>% 
  group_by(Subject) %>% 
  tally()%>% 
  ungroup() %>% 
  summarise(mean_tok = mean(n),
            sd_tok = sd(n))

mean_typ_disyl <- disyl_data %>% 
  group_by(Subject, Gloss) %>% 
  tally() %>%
  ungroup() %>%
  group_by(Subject) %>% 
  tally() %>% 
  summarise(mean_typ = mean(n),
            sd_typ = sd(n))

```

```{r table 1}

infants <- main_data %>% group_by(Language, Subject) %>% slice(1) %>% ungroup() %>%
  group_by(Language) %>% tally()

ages <- main_data %>% 
  group_by(Language) %>% 
  summarise(mean_age = mean(Age),
            sd_age = sd(Age)) %>%
  dplyr::select(-Language)

n_typ <- main_data %>% group_by(Subject, Language, Gloss) %>% tally() %>%
  ungroup() %>%
  group_by(Language, Subject) %>% 
  tally() %>% 
  summarise(mean_typ = mean(n),
            sd_typ = sd(n)) %>%
  dplyr::select(-Language)

n_tok <- main_data %>% 
  group_by(Language,Subject) %>% 
  tally() %>% 
  summarise(mean_tok = mean(n), 
            sd_tok = sd(n)) %>%
  dplyr::select(-Language)

n_typ_disyl <- disyl_data %>% group_by(Subject, Language, Gloss) %>% tally() %>%
  ungroup() %>%
  group_by(Language, Subject) %>% 
  tally() %>% 
  summarise(mean_typ_di = mean(n),
            sd_typ_di = sd(n)) %>%
  dplyr::select(-Language)

n_tok_disyl <- disyl_data %>% 
  group_by(Language,Subject) %>% 
  tally() %>% 
  summarise(mean_tok_di = mean(n), 
            sd_tok_di = sd(n)) %>%
  dplyr::select(-Language)

Table1 <- cbind(infants, ages, n_typ, n_tok, n_typ_disyl, n_tok_disyl) %>%
  mutate_if(is.numeric, ~round(., 2)) %>%
  mutate(sd_age = paste0("(", sd_age, ")"),
         sd_typ = paste0("(", sd_typ, ")"),
         sd_tok = paste0("(", sd_tok, ")"),
         sd_typ_di = paste0("(", sd_typ_di, ")"),
         sd_tok_di = paste0("(", sd_tok_di, ")")) %>%
  unite("Mean age (SD)", mean_age, sd_age, sep = " ") %>%
  unite("Mean word types (SD)", mean_typ, sd_typ, sep = " ") %>%
  unite("Mean word tokens (SD)", mean_tok, sd_tok, sep = " ") %>%
  unite("Mean word types (SD) (disyl. targets)", mean_typ_di, sd_typ_di, sep = " ") %>%
  unite("Mean word tokens (SD) (disyl. targets)", mean_tok_di, sd_tok_di, sep = " ") %>%
  rename("n infants" = n)

kable(Table1) %>% kable_styling("striped") %>% save_kable("Table1.pdf")
```

```{r syllable numbers - Table 2}

distance_data %>% filter(data_type == "actual" & nsyl_actual == 2)

distance_data %>% filter(data_type == "actual" & nsyl_actual == 2) %>% 
  tally() %>% 
  summarise(n_disyl = sum(n),
            pc_disyl = n_disyl/1794)

prop_syls <- distance_data %>% filter(data_type == "actual") %>% 
  group_by(nsyl_actual) %>% 
  tally() %>%  
  mutate(prop = n/1794) %>%
  mutate_if(is.numeric, ~round(., 2)) %>%
  rename("proportion" = prop) %>%
  dplyr::select(-n)

Table2 <- distance_data %>% filter(data_type == "actual") %>% 
  group_by(Language, nsyl_actual) %>% tally() %>% 
  pivot_wider(names_from = Language, values_from = n) %>%
  mutate_all(~replace(., is.na(.), 0)) %>%
  left_join(prop_syls) %>%
  rename("n syllables" = nsyl_actual)

  
kable(Table2) %>% kable_styling("striped") %>% save_kable("Table2.pdf")

```

```{r ex of distance table}

Table3 <- distance_data %>% dplyr::select(Subject, Language, Gloss, IPAactual, 
                                S1C1.S1C1, #S1C2.S1C2, S1C3.S1C3, S1C4.S1C4,
                                S2C1.S2C1, #S2C2.S2C2, S2C3.S2C3, S2C4.S2C4,
                                SFC1.SFC1, #SFC2.SFC2, 
                                SFCF1.SFCF1, #SFCF2.SFCF2,
                                nsyl_actual, data_type
                                ) %>%
  filter(#S1C1.S1C1 != "0" &
           #nsyl_actual ==2 &
             data_type == "actual" & 
             Language == "UK") %>%
  group_by(Gloss) %>%
  slice(1) %>%
  filter(Gloss %in% c("cuddle", "cookie", "phuppo", "eeyore", "flowers")) %>%
  dplyr::select(-nsyl_actual, -data_type) %>%
  rename("IPA" = IPAactual)

names(Table3) <- sub(".*.", "", names(Table3))
names(Table3)

kable(Table3) %>% kable_styling("striped") %>% save_kable("Table3.pdf")

```

```{r ex of distance table - geminates}
#set.seed(24)

Table4a <- distance_data %>%
  filter(
    geminate_T == T,
    data_type == "target") %>%
  group_by(Language, Gloss)  %>%
  slice(1) %>%
  mutate(`Data type` = ifelse(Subject == "Atte", "Target", "")
         ) %>%
  dplyr::select(`Data type`,Subject, Language, Gloss, IPAtarget,
                                S1C1.S1C1, #S1C2.S1C2, S1C3.S1C3, S1C4.S1C4,
                                S1CF1.S1CF1, S1CF2.S1CF2,
                                S2C1.S2C1, S2CF1.S2CF1, #S2C2.S2C2, S2C3.S2C3, S2C4.S2C4,
                                SFC1.SFC1, #SFC2.SFC2,
                                #SFCF1.SFCF1, SFCF2.SFCF2,
                                ) %>%
  filter(Gloss %in% c("ankka", "hot", "cookie", "phuppo")) %>%
  rename("IPA" = IPAtarget) %>%
  mutate(Gloss = fct_recode(Gloss,
                            "ankka 'duck'" = "ankka",
                            "kukki 'cookie'" = "cookie",
                            "atsui 'hot" = "hot",
                            "phuppo 'uncle'" = "phuppo"),
         )

names(Table4a) <- sub(".*.", "", names(Table4a))
names(Table4a)

Table4b <- distance_data %>%
  filter(
    geminate_A == T,
    data_type == "actual") %>%
  group_by(Language, Gloss)  %>%
  slice(1) %>%
  mutate(`Data type` = ifelse(Subject == "Mira", "Actual", "")
         ) %>%
  dplyr::select(`Data type`, Subject, Language, Gloss, IPAactual,
                                S1C1.S1C1, #S1C2.S1C2, S1C3.S1C3, S1C4.S1C4,
                                S1CF1.S1CF1, S1CF2.S1CF2,
                                S2C1.S2C1, S2CF1.S2CF1,#S2C2.S2C2, S2C3.S2C3, S2C4.S2C4,
                                SFC1.SFC1, #SFC2.SFC2,
                                #SFCF1.SFCF1, SFCF2.SFCF2
                                ) %>%
   filter(Gloss %in% c("häntä", "roska", "cassé", "Mummy")) %>%
   rename("IPA" = IPAactual) %>%
  mutate(Gloss = fct_recode(Gloss,
                            "häntä 'him'" = "häntä",
                            "roska 'rubbish'" = "roska",
                            "cassé 'broken" = "cassé"))

names(Table4b) <- sub(".*.", "", names(Table4b))
names(Table4b)

Table4 <- rbind(Table4a, Table4b)

kable(Table4) %>% kable_styling("striped") %>% save_kable("Table4.pdf")

```



```{r distance matrix}

#source("mini_matrix.R")

```


```{r iterative networks analysis}

smallworlddata_it <- read_csv("globalsmallworlddata_iter.csv")

```


```{r Table 5}

Table5_base <- smallworlddata_it %>%
  dplyr::select(-Speaker, -Speaker_ID, -ID) %>%
  group_by(Language, data_type) %>%
  summarise(mean_CC = mean(clust_coef_global),
            #sd_CC = sd(clust_coef_global),
            mean_k = mean(mean_k),
           # sd_k = sd(mean_k),
            mean_PL = mean(path_length)
            #sd_PL = sd(path_length)
            ) %>% 
  pivot_wider(names_from = data_type,
    values_from = c(mean_CC, mean_k, mean_PL)
  )%>%
   mutate_if(is.numeric, ~round(., 2)) #%>%
  # mutate(mean_CC_iter_A = as.character(mean_CC_iter_A),
  #        mean_CC_iter_T = as.character(mean_CC_iter_T),
  #        mean_k_iter_T = as.character(mean_k_iter_T),
  #        mean_k_iter_A = as.character(mean_k_iter_A),
  #        mean_PL_iter_A = as.character(mean_PL_iter_A),
  #        mean_PL_iter_T = as.character(mean_PL_iter_T))

Table5_means <-  Table5_base %>% 
  ungroup() %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>%
 # mutate(Language = "Mean") %>% 
  pivot_longer(
  cols = 1:6,
  names_to = "var",
  values_to = "mean"
  )

Table5_sd <-  Table5_base %>%
  ungroup() %>%
  summarise_if(is.numeric, sd, na.rm = TRUE) %>%
    pivot_longer(
  cols = 1:6,
  names_to = "var",
  values_to = "sd"
  )

Table5_mean_sd <- cbind(Table5_means, Table5_sd) %>%
  dplyr::select(-3) %>%
  mutate_if(is.numeric, ~round(., 2)) %>%
  mutate(sd = paste0("(", sd, ")")) %>%
  unite("Mean (SD)", mean, sd, sep = " ") %>%
  pivot_wider(names_from = var,
    values_from = "Mean (SD)") %>%
  mutate(Language = "Mean (SD)")

Table5 <- Table5_base %>%
  mutate(mean_CC_iter_A = as.character(mean_CC_iter_A),
         mean_CC_iter_T = as.character(mean_CC_iter_T),
         mean_k_iter_T = as.character(mean_k_iter_T),
         mean_k_iter_A = as.character(mean_k_iter_A),
         mean_PL_iter_A = as.character(mean_PL_iter_A),
         mean_PL_iter_T = as.character(mean_PL_iter_T)) %>%
  rbind(Table5_mean_sd) %>%
  rename(
    "Clustering coeff. (A)" = mean_CC_iter_A,
    "Clustering coeff. (T)" = mean_CC_iter_T,
    "Mean k (A)" = mean_k_iter_A,
    "Mean k (T)" = mean_k_iter_T,
    "Path length (A)" = mean_PL_iter_A,
    "Path length (T)" = mean_PL_iter_T
  )

kable(Table5) %>% kable_styling("striped") %>% save_kable("Table5.pdf")
```

```{r}

# disyl_data %>% group_by(Subject) %>% tally() %>% summarise(min = min(n),
#                                                            max = max(n))

it_summary_networks <- smallworlddata_it %>% 
  group_by(Speaker, Language) %>%
  summarise(path_length = mean(path_length),
            mean_k = mean(mean_k),
            clust_coef = mean(clust_coef_global))

network_graphs_long <- smallworlddata_it %>% pivot_longer(
  cols = path_length:clust_coef_global,
  names_to = "var",
  values_to = "value"
) #%>%
  # group_by(Speaker, var, Language, data_type) %>%
  # summarize(value = mean(value))

Fig1 <- network_graphs_long %>%
  mutate(var = fct_recode(var,
                          "Clustering coefficient" = "clust_coef_global",
                          "Mean k" = "mean_k",
                          "Path length" = "path_length"),
        data_type = fct_recode(data_type,
        "Actual" = "iter_A",
        "Target" = "iter_T")) %>%
  ggplot(aes(x = Language, y = value, colour = data_type)) +
  geom_boxplot(aes(fill = data_type), alpha = .8) +
  geom_point(shape = 1, position = position_jitterdodge(), alpha=.1) +
  scale_colour_brewer(palette = "Set1") +
  theme_bw(base_size = 14) +
  theme(legend.title = element_blank(),
        axis.text.x = element_text(angle = 45, vjust = 0.7)) +
  facet_wrap(~var, ncol = 3, scales = "free")


```

Fig1
```{r top and bottom infants}

top_infants_meank <- it_summary_networks %>%
  arrange(desc(mean_k)) %>%
  head(5) %>%
  dplyr::select(mean_k, Speaker, Language) %>%
  mutate(Measure = "Mean k") %>%
  rename("Value" = mean_k)

top_infants_PL <- it_summary_networks %>%
  arrange(path_length) %>%
  head(5) %>%
  dplyr::select(path_length, Speaker, Language) %>%
  mutate(Measure = "Path length") %>%
  rename("Value" = path_length)

top_infants_CC <- it_summary_networks %>%
  arrange(desc(clust_coef)) %>%
  head(5) %>%
  dplyr::select(clust_coef, Speaker, Language) %>%
  mutate(Measure = "Clust. coef.") %>%
  rename("Value" = clust_coef)

top_infants <- rbind(top_infants_CC, top_infants_meank, top_infants_PL) %>%
  mutate_if(is.numeric, ~round(., 2)) %>%
  dplyr::select(Measure, Speaker, Language, Value)

bottom_infants_meank <- it_summary_networks %>%
  arrange(mean_k) %>%
  head(5) %>%
  dplyr::select(mean_k, Speaker, Language) %>%
  mutate(Measure = "Mean k",) %>%
  rename("Value" = mean_k)

bottom_infants_PL <- it_summary_networks %>%
  arrange(desc(path_length)) %>%
  head(5) %>%
  dplyr::select(path_length, Speaker, Language) %>%
  mutate(Measure = "Path length") %>%
  rename("Value" = path_length)

bottom_infants_CC <- it_summary_networks %>%
  arrange(clust_coef) %>%
  head(5) %>%
  dplyr::select(clust_coef, Speaker, Language) %>%
  mutate(Measure = "Clust. coef.") %>%
  rename("Value" = clust_coef)

bottom_infants <- rbind(bottom_infants_CC, bottom_infants_meank, bottom_infants_PL) %>%
  mutate_if(is.numeric, ~round(., 2)) %>%
  dplyr::select(Measure, Speaker, Language, Value)

kable(bottom_infants) %>% kable_styling("striped") %>% save_kable("Table6b.pdf")
kable(top_infants) %>% kable_styling("striped") %>% save_kable("Table6a.pdf")

  
```


```{r network graphs for top infants - mean k and clustering coef}

options(ggrepel.max.overlaps = Inf)

carys_01_tab <- read.table("carys_01_A.txt",header=TRUE,row.names=1)   ### need to update these

carys_01 <- as.matrix(carys_01_tab)

words_carys_01 <- as.data.frame(dimnames(carys_01))

words_carys_01_alph <- gsub('[0-9.]', '', words_carys_01[1])

dimnames(carys_01) <- list(NULL, c("gaggag", "lorry", "tata", "tata", "hiya", "tedi", "eisio", "tractor", "eisio", "hwnna", "Meira", "eira", "Lucy", "tedi", "eira", "hiya", "hwnna", "La-La", "tedi", "Meira"))
  

# standardize values

Q1_carys_01 <- quantile(carys_01[carys_01 > 0], 0.25)

carys_01 <- ifelse(carys_01>Q1_carys_01, NA, carys_01)
carys_01 <- ifelse(carys_01==0, 0.1, carys_01)


# Transform it in a network graph format
network_carys_01 <- graph_from_adjacency_matrix(carys_01, weighted = TRUE, diag=F)

# Remove edges with NA weights
network_carys_01 <- delete_edges(network_carys_01, 
                                  E(network_carys_01)[is.na(E(network_carys_01)$weight)])

flip <- function(x) max(x)-x+1  # function to flip the values so that wider edges = closer connection

# Make the graph
carys_01_graph <- ggraph(network_carys_01) +
  geom_edge_link(aes(edge_width=(edge_width=flip(weight)),
                     edge_colour = weight),
                # edge_colour="grey", 
                 edge_alpha=0.2) +
  geom_node_point(fill="#69b3a2", 
                  colour = "grey36",
                  size=3, stroke = 1.2, shape = 21) +
  geom_node_text(aes(label=name),
                 repel = TRUE, size=4#, color="#69b3a2"
                 ) +
  theme_void(base_size = 14) +
  ggtitle("3a. Carys: Highest clustering coefficient") +
  theme(
    legend.position="none",
    plot.margin=unit(rep(1,4), "cm")
    
carys_01_graph2 <- ggraph(network_carys_01) +
  geom_edge_link(aes(edge_width=(edge_width=flip(weight)),
                     edge_colour = weight),
                # edge_colour="grey", 
                 edge_alpha=0.2) +
  geom_node_point(fill="#69b3a2", 
                  colour = "grey36",
                  size=3, stroke = 1.2, shape = 21) +
  geom_node_text(aes(label=name),
                 repel = TRUE, size=4#, color="#69b3a2"
                 ) +
  theme_void(base_size = 14) +
  ggtitle("3c. Carys: Highest mean k") +
  theme(
    legend.position="none",
    plot.margin=unit(rep(1,4), "cm")
  )

```
carys_01_graph
carys_01_graph2

```{r network graphs for top infants - path length}

adeline_01_tab <- read.table("adeline_01_A.txt",header=TRUE,row.names=1)   ### need to update these

adeline_01 <- as.matrix(adeline_01_tab)

words_adeline_01 <- as.data.frame(dimnames(adeline_01))

words_adeline_01_alph <- gsub('[0-9.]', '', words_adeline_01[1])

dimnames(adeline_01) <- list(NULL, c("encore", "encore", "au revoir", "au revoir", "au revoir", "encore", "encore", "au revoir", "encore", "voiture", "chapeau", "encore", "encore", "maman", "bisou", "coucou", "encore", "coucou", "encore", "oiseau"))
  

# standardize values

Q1_adeline_01 <- quantile(adeline_01[adeline_01 > 0], 0.25)

adeline_01 <- ifelse(adeline_01>Q1_adeline_01, NA, adeline_01)
adeline_01 <- ifelse(adeline_01==0, 0.1, adeline_01)


# Transform it in a network graph format
network_adeline_01 <- graph_from_adjacency_matrix(adeline_01, weighted = TRUE, diag=F)

# Remove edges with NA weights
network_adeline_01 <- delete_edges(network_adeline_01, 
                                  E(network_adeline_01)[is.na(E(network_adeline_01)$weight)])

flip <- function(x) max(x)-x+1  # function to flip the values so that wider edges = closer connection

# Make the graph
adeline_01_graph <- ggraph(network_adeline_01, layout = "stress") +
  geom_edge_link(aes(edge_width=(edge_width=flip(weight)),
                     edge_colour = weight),
                # edge_colour="grey", 
                 edge_alpha=0.2) +
  geom_node_point(fill="#69b3a2", 
                  colour = "grey36",
                  size=3, stroke = 1.2, shape = 21) +
  geom_node_text(aes(label=name),
                 repel = TRUE, size=4#, color="#69b3a2"
                 ) +
  theme_void(base_size = 14) +
  ggtitle("3e. Adeline: Lowest path length") +
  theme(
    legend.position="none",
    plot.margin=unit(rep(1,4), "cm")
  )

```

adeline_01_graph

```{r network graphs for bottom infants - clustering coefficient}

lewis_01_tab <- read.table("lewis_01_A.txt",header=TRUE,row.names=1)   ### need to update these

lewis_01 <- as.matrix(lewis_01_tab)

words_lewis_01 <- as.data.frame(dimnames(lewis_01))

words_lewis_01_alph <- gsub('[0-9.]', '', words_lewis_01[1])

dimnames(lewis_01) <- list(NULL, c("choo-choo", "all gone", "choo-choo", "choo-choo", "ladder", "oh no", "all gone", "circle", "uh-oh", "oh no", "all gone", "oh no", "all gone", "all gone", "all gone", "choo-choo", "uh-oh", "uh-oh", "woof woof", "oh no"))
  

# standardize values

Q1_lewis_01 <- quantile(lewis_01[lewis_01 > 0], 0.25)

lewis_01 <- ifelse(lewis_01>Q1_lewis_01, NA, lewis_01)
lewis_01 <- ifelse(lewis_01==0, 0.1, lewis_01)


# Transform it in a network graph format
network_lewis_01 <- graph_from_adjacency_matrix(lewis_01, weighted = TRUE, diag=F)

# Remove edges with NA weights
network_lewis_01 <- delete_edges(network_lewis_01, 
                                  E(network_lewis_01)[is.na(E(network_lewis_01)$weight)])

flip <- function(x) max(x)-x+1  # function to flip the values so that wider edges = closer connection

# Make the graph
lewis_01_graph <- ggraph(network_lewis_01, layout = "stress") +
  geom_edge_link(aes(edge_width=(edge_width=flip(weight)),
                     edge_colour = weight),
                # edge_colour="grey", 
                 edge_alpha=0.2) +
  geom_node_point(fill="#69b3a2", 
                  colour = "grey36",
                  size=3, stroke = 1.2, shape = 21) +
  geom_node_text(aes(label=name),
                 repel = TRUE, size=4#, color="#69b3a2"
                 ) +
  theme_void(base_size = 14) +
  ggtitle("3b. Lewis: Lowest clustering coefficient") +
  theme(
    legend.position="none",
    plot.margin=unit(rep(1,4), "cm")
  )
```
lewis_01_graph
```{r network graphs for bottom infants - mean k}

tobias_01_tab <- read.table("tobias_01_A.txt",header=TRUE,row.names=1)   ### need to update these

tobias_01 <- as.matrix(tobias_01_tab)

words_tobias_01 <- as.data.frame(dimnames(tobias_01))

words_tobias_01_alph <- gsub('[0-9.]', '', words_tobias_01[1])

dimnames(tobias_01) <- list(NULL, c("peacock", "monkey", "quack quack", "quack quack", "quack quack", "tortoise", "ribbit ribbit", "baby", "what's that", "eeyore", "neenaw", "eeyore", "toot toot", "quack quack", "monkey", "quack quack", "quack quack", "honk honk", "woof woof", "what's that"))
  

# standardize values

Q1_tobias_01 <- quantile(tobias_01[tobias_01 > 0], 0.25)

tobias_01 <- ifelse(tobias_01>Q1_tobias_01, NA, tobias_01)
tobias_01 <- ifelse(tobias_01==0, 0.1, tobias_01)


# Transform it in a network graph format
network_tobias_01 <- graph_from_adjacency_matrix(tobias_01, weighted = TRUE, diag=F)

# Remove edges with NA weights
network_tobias_01 <- delete_edges(network_tobias_01, 
                                  E(network_tobias_01)[is.na(E(network_tobias_01)$weight)])

flip <- function(x) max(x)-x+1  # function to flip the values so that wider edges = closer connection

# Make the graph
tobias_01_graph <- ggraph(network_tobias_01, layout = "stress") +
  geom_edge_link(aes(edge_width=(edge_width=flip(weight)),
                     edge_colour = weight),
                # edge_colour="grey", 
                 edge_alpha=0.2) +
  geom_node_point(fill="#69b3a2", 
                  colour = "grey36",
                  size=3, stroke = 1.2, shape = 21) +
  geom_node_text(aes(label=name),
                 repel = TRUE, size=4#, color="#69b3a2"
                 ) +
  theme_void(base_size = 14) +
  ggtitle("3d. Tobias: Lowest mean k") +
  theme(
    legend.position="none",
    plot.margin=unit(rep(1,4), "cm")
  )
```

tobias_01_graph

```{r network graphs for bottom infants - [mean path length}

sini_01_tab <- read.table("sini_01_A.txt",header=TRUE,row.names=1)   ### need to update these

sini_01 <- as.matrix(sini_01_tab)

words_sini_01 <- as.data.frame(dimnames(sini_01))

words_sini_01_alph <- gsub('[0-9.]', '', words_sini_01[1])

dimnames(sini_01) <- list(NULL, c("kakku", "täti", "mummi", "kynä", "ukki", "leipä", "viili", "pupu", "loppu", "kiikkaa", "loppu", "heihei", "rikki", "kukka", "tyttö", "kirja", "tyttö", "roska", "hauhau", "sakset"))
  

# standardize values

Q1_sini_01 <- quantile(sini_01[sini_01 > 0], 0.25)

sini_01 <- ifelse(sini_01>Q1_sini_01, NA, sini_01)
sini_01 <- ifelse(sini_01==0, 0.1, sini_01)


# Transform it in a network graph format
network_sini_01 <- graph_from_adjacency_matrix(sini_01, weighted = TRUE, diag=F)

# Remove edges with NA weights
network_sini_01 <- delete_edges(network_sini_01, 
                                  E(network_sini_01)[is.na(E(network_sini_01)$weight)])

flip <- function(x) max(x)-x+1  # function to flip the values so that wider edges = closer connection

# Make the graph
sini_01_graph <- ggraph(network_sini_01, layout = "stress") +
  geom_edge_link(aes(edge_width=(edge_width=flip(weight)),
                     edge_colour = weight),
                # edge_colour="grey", 
                 edge_alpha=0.2) +
  geom_node_point(fill="#69b3a2", 
                  colour = "grey36",
                  size=3, stroke = 1.2, shape = 21) +
  geom_node_text(aes(label=name),
                 repel = TRUE, size=4#, color="#69b3a2"
                 ) +
  theme_void(base_size = 14) +
  ggtitle("3f. Sini: Highest path length") +
  theme(
    legend.position="none",
    plot.margin=unit(rep(1,4), "cm")
  )
```

sini_01_graph

### OLD


```{r network graphs - summary}

network_graphs_long <- network_graphs %>% pivot_longer(
  cols = path_length:clust_coef_global,
  names_to = "var",
  values_to = "value"
)

Fig1 <- network_graphs_long %>%
  filter(!is.na(Speaker)) %>%
  mutate(var = fct_recode(var,
                          "Clustering coefficient" = "clust_coef_global",
                          "Mean k" = "mean_k",
                          "Path length" = "path_length")) %>%
  ggplot(aes(x = Language, y = value, colour = data_type)) +
  geom_boxplot(aes(fill = data_type), alpha = .1) +
  geom_point(shape = 1, position = position_jitterdodge()) +
  scale_colour_brewer(palette = "Set1") +
  theme_bw(base_size = 14) +
  theme(legend.title = element_blank(),
        axis.text.x = element_text(angle = 45, vjust = 0.7)) +
  facet_wrap(~var, ncol = 3, scales = "free")
```

Fig1


# Fig2 <- ggplot(smallworlddata_it, aes(mean_k, path_length, group = Speaker)) +
#   geom_point(aes(colour = Speaker), shape = 1, alpha = 0.8, position = position_jitter()) +
#     geom_point(data = it_summary_networks, aes(fill = Speaker), shape = 21, size = 3) +
#   xlab("Mean k") +
#   ylab("Mean path length") +
#   theme_bw(base_size = 12) +
#   theme(legend.position="none") +
#   facet_wrap(~Language, ncol = 3)